Supplement: Bootstrapping Domain Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-09 supplement.tex
another text problem example
reorganize text examples

We automatically generated 600 string editing problems split 75/25 train/test.
We show representative problems:
\pagebreak

double

\begin{tabular}{ll}
        \toprule Input&Output\\\midrule
vlxS & vlxSvlxS \\
 JkVC & JkVCJkVC \\
 dbxD & dbxDdbxD \\
 gQgB & gQgBgQgB
\\\bottomrule
\end{tabular}

Extract string delimited by ',' (inclusive),' '
\begin{tabular}{ll}
        \toprule Input&Output\\\midrule
LsR,uhMZI wIL & ,uhMZI  \\
 tMY,KdF hhT & ,KdF  \\
 UUPdC,UAd kCgtq & ,UAd  \\
 gQgGN,VMJ FjrXZ & ,VMJ 
\\\bottomrule
\end{tabular}

Apply first 2 characters to input delimited by '.'
\begin{tabular}{ll}
        \toprule Input&Output\\\midrule
OhCQN.DlH.LdkJ.pLh & OhDlLdpL \\
 CZr.mveZr.dvjP.YMJpg & CZmvdvYM \\
 bpub.VkkZ.dYdPr & bpVkdY \\
 zjNA.wFwY.WMMqh.OFdbr & zjwFWMOF
\\\bottomrule
\end{tabular}

Apply first 2 characters to string delimited by ' ','.'
\begin{tabular}{ll}
        \toprule Input&Output\\\midrule
fNA YWyL.JDD & YW \\
 YWozt TPW.nczz & TP \\
 RJwiT dpW.uFU & dp \\
 FTp gNMo.JsZB & gN
\\\bottomrule
\end{tabular}

%% Apply double to input delimited by '.'
%% \begin{tabular}{ll}
%%         \toprule Input&Output\\\midrule
%% FWhb.jYMdi & FWhbFWhbjYMdijYMdi \\
%%  JZB.WEwgH & JZBJZBWEwgHWEwgH \\
%%  SgA.Kxo.RyF & SgASgAKxoKxoRyFRyF \\
%%  NMApj.OaPBs.uZm.iCZy & NMApjNMApjOaPBsOaPBsuZmuZmiCZyiCZy
%% \\\bottomrule
%% \end{tabular}

Apply strip to string delimited by ',','.'
\begin{tabular}{ll}
        \toprule Input&Output\\\midrule
iNEP,  GigW .Xlm & GigW \\
 xhpH,  QvwnW .mfK & QvwnW \\
 weWIC,IQjhWa .fGKz & IQjhWa \\
 xZUm, FpdE.ETcr & FpdE
\\\bottomrule
\end{tabular}

drop first character

\begin{tabular}{ll}
        \toprule Input&Output\\\midrule
WYPvm & YPvm \\
 terHk & erHk \\
 asWM & sWM \\
 tBdT & BdT
\\\bottomrule
\end{tabular}

@@

>>>>

@@

We automatically generated 600 string editing problems split 75/25 train/test.
The following are representative problems:
\pagebreak

\begin{center}
\begin{tabular}{|l|l|}
  \hline Input&Output\\
  \hline\multicolumn{2}{|c|}{Double}\\
  \hline
vlxS & vlxSvlxS \\
 JkVC & JkVCJkVC \\
 dbxD & dbxDdbxD \\
 gQgB & gQgBgQgB \\
  \hline\multicolumn{2}{|c|}{Extract string delimited by ',' (inclusive),' '}\\
  \hline
LsR,uhMZI wIL & ,uhMZI  \\
 tMY,KdF hhT & ,KdF  \\
 UUPdC,UAd kCgtq & ,UAd  \\
 gQgGN,VMJ FjrXZ & ,VMJ \\
  \hline\multicolumn{2}{|c|}{Apply first 2 characters to input delimited by '.'}\\
  \hline
OhCQN.DlH.LdkJ.pLh & OhDlLdpL \\
 CZr.mveZr.dvjP.YMJpg & CZmvdvYM \\
 bpub.VkkZ.dYdPr & bpVkdY \\
 zjNA.wFwY.WMMqh.OFdbr & zjwFWMOF \\
  \hline\multicolumn{2}{|c|}{Apply first 2 characters to string delimited by ' ','.'}\\
  \hline
fNA YWyL.JDD & YW \\
 YWozt TPW.nczz & TP \\
 RJwiT dpW.uFU & dp \\
 FTp gNMo.JsZB & gN \\
%  \hline\multicolumn{2}{|c|}{Apply double to input delimited by '.'}\\
%  \hline
%FWhb.jYMdi & FWhbFWhbjYMdijYMdi \\
% JZB.WEwgH & JZBJZBWEwgHWEwgH \\
% SgA.Kxo.RyF & SgASgAKxoKxoRyFRyF \\
% NMApj.OaPBs.uZm.iCZy & NMApjNMApjOaPBsOaPBsuZmuZmiCZyiCZy \\
  \hline\multicolumn{2}{|c|}{Apply strip to string delimited by ',','.'}\\
  \hline
iNEP,  GigW .Xlm & GigW \\
 xhpH,  QvwnW .mfK & QvwnW \\
 weWIC,IQjhWa .fGKz & IQjhWa \\
 xZUm, FpdE.ETcr & FpdE \\
  \hline\multicolumn{2}{|c|}{Drop first character}\\
  \hline
WYPvm & YPvm \\
 terHk & erHk \\
 asWM & sWM \\
 tBdT & BdT \\
\hline
\end{tabular}
\end{center}
